---
title: "ggtaxplot"
description: "Process and Plot Taxonomic Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggtaxplot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette demonstrates how to use the `ggtaxplot` package to process and visualize taxonomic data.

# Installation
You can install the package from GitLab using the following command:

```{r setup_install}
devtools::install_git("https://gitlab.com/ccoclet/ggtaxplot.git")
```

# Example Usage

## Load the Package

```{r setup_load}
library(ggtaxplot)
```

## Example Data

Here is an example dataset:
```{r example_data}
data <- data.frame(
    ID = c("ID1", "ID2", "ID3"),
    Taxonomy = c("d__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Enterobacterales;f__Enterobacteriaceae;g__Escherichia",
                 "d__Bacteria;p__Firmicutes;c__Bacilli;o__Bacillales;f__Bacillaceae;g__Bacillus",
                 "d__Bacteria;p__Actinobacteria;c__Actinobacteria;o__Corynebacteriales;f__Corynebacteriaceae;g__Corynebacterium")
)
```

## Generate the Plot
```{r generate_plot}
plot <- ggtaxplot(data)
print(plot)
```

# Conclusion

This vignette provided an overview of how to use the `ggtaxplot` package. For more details, refer to the package documentation.